An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-22 paper.tex
update the introduction part

Breadth-first search is probably the most basic graph searching algorithm and
it is also the building block of other graph algorithms like minimum spanning tree
and shortest path \cite{ckrs09}.
Despite the fact that graph metrics \cite{ntmm13,tmml09,tsmm09} and
various centrality measures like Katz centrality~\cite{gphe11,grihig13},
betweenness \cite{alhi15}, and closeness \cite{tmml10})
have been generalized for evolving graphs,
a BFS for evolving graphs, which we shall call it \emph{evolving-graph BFS},
was never explicitly described or verified.

@@

\begin{thm}[Correctness of evolving-graph BFS]
Let an evolving graph $G_n$ and a starting node $(s,t_0)$ be given.
The evolving-graph BFS discovers every active node that is reachable from the source $(s,t_0)$ and $d.(v, t)$ is the length of the shortest temporal path
from $(s,t_0)$ to $(v,t)$.
\end{thm}
\proof
We could map an evolving graph $G_n$ to a static graph $G$ in such a way that
if there is an edge from $(v, t)$ to $(u,t)$ in $G_n$, there is an edge from $v_t$ to $u_t$ in $G$.
For any two nodes $v_s$ and $v_t$ in $G$,  if $s < t$, we add an edge from $v_s$ to $v_t$.
By construction, the forward-neighbors of an active node $(v, t)$ in $G_n$
are in one-to-one correspondence with the forward-neighbors of a node $v_t$ in $G$.
Hence the correctness of the evolving graph BFS follows from that of a static graph.
\endproof

>>>>

Breadth-first search (BFS) is probably the most basic graph searching algorithm and
it is also the building block of other graph algorithms like minimum spanning tree
and shortest path \cite{ckrs09}.
Despite the fact that graph metrics \cite{ntmm13,tmml09,tsmm09} and
various centrality measures like Katz centrality~\cite{gphe11,grihig13},
betweenness \cite{alhi15}, and closeness \cite{tmml10})
have been generalized for evolving graphs,
a BFS for evolving graphs, which we shall call it \emph{evolving-graph BFS},
was never explicitly described or verified.
Therefore, there is a need for clear presentations of the algorithm.

@@

\begin{thm}[Correctness of evolving-graph BFS]
Let an evolving graph $G_n$ and a starting node $(s,t_0)$ be given.
The evolving-graph BFS discovers every active node that is reachable from the source $(s,t_0)$ and $dict.(v, t)$ is the length of the shortest temporal path
from $(s,t_0)$ to $(v,t)$.
\end{thm}
\proof
We could map an evolving graph $G_n$ to a static graph $G$ in such a way that
if there is an edge from $(v, t)$ to $(u,t)$ in $G_n$, there is an edge from $v_t$ to $u_t$ in $G$.
For any two nodes $v_s$ and $v_t$ in $G$,  if $s < t$, we add an edge from $v_s$ to $v_t$.
By construction, the forward-neighbors of an active node $(v, t)$ in $G_n$
are in one-to-one correspondence with the forward-neighbors of a node $v_t$ in $G$.
Hence the correctness of the evolving graph BFS follows from that of a static graph.
\endproof
